Wind_analyses

### 2019-04-03 Wind_analyses.Rmd
Still to do some minor fixing

wind_data <- rbind(wind_3_HoutBay,wind_sitesmatched_3,wind_sitesmatched_2,wind_sitesmatched_1)
wind_data <- wind_data %>% 
  dplyr::rename(site = temp_sites) %>% 
  mutate(date = as.Date(date)) %>% 
  mutate(hour = as.numeric(hour),
         dir = as.numeric(dir),
         speed = as.numeric(speed)) %>% 
  select(site, date, hour, dir, speed)

# save(wind_data, file = "Data/wind_data.RData")

@@

wind_daily <- wind_data %>%
  mutate(date = as.Date(date)) %>%
  group_by(site, date) %>%
  summarise(dir_circ = mean.circular(circular(dir, units = "degrees")),
            mean_speed = mean(speed))

# save(wind_daily, file = "Data/wind_daily.RData")

load("Data/wind_daily.RData") # Loading the daily wind data for each of the sites
```

@@

# Select only the years 2014 and 2015
filtered_years <- function(df){
  upwelling<- df %>% 
  filter(year(date) %in% seq(2014, 2015)) %>% 
  drop_na()
}

@@

temp_wind <- function(df){
  combined <- df %>% 
  left_join(wind_daily, by = c("site", "date")) %>% 
  #select(-combi) %>% 
  na.trim()
  return(combined)
}

temp_wind_MUR <- temp_wind(df = MUR_fyears) %>% 
  drop_na()
temp_wind_SACTN <- temp_wind(df = SACTN_fyears)
temp_wind_OISST <- temp_wind(df = OISST_fyears)
temp_wind_G1SST <- temp_wind(df = G1SST_fyears)
temp_wind_K10 <- temp_wind(df = K10_fyears)

speed_plot <- temp_wind_MUR %>% 
  select(lat, lon, mean_speed) %>% 
  group_by(lat, lon) %>% 
  summarise(max_speed = max(mean_speed)) %>% 
  summarise(lat = round(lat, na.rm = T),3)#%>% 
  # dplyr::rename(Z = "mean_speed") %>% 
  # dplyr::rename(X = "lat") %>% 
  # dplyr::rename(Y = "lon")

 maxw <- cbind(speed_plot$lon, speed_plot$lat, speed_plot$max_speed)  
head(maxw)

rmax <- rasterFromXYZ(maxw)  
 acol <- colorRampPalette(c("white", "blue", "darkblue"))  
 plot(rmax, col=acol(1000), main= "Maximum wind speed reported",  
     xlab="Longitude", ylab="Lattitude")  + lines(getMap(resolution = "high"), lwd=2)

 library(rworldmap)  
 lines(getMap(resolution = "high"), lwd=2)  
```

>>>>

wind_data <- rbind(wind_3_HoutBay,wind_sitesmatched_3,wind_sitesmatched_2,wind_sitesmatched_1)
wind_data <- wind_data %>% 
  drop_na()
save(wind_data, file = "Data/wind_data.RData")

@@

wind_data <- wind_data %>% 
  as.numeric(dir)

wind_data <- wind_data %>%
  mutate(date = as.Date(date)) %>%
  group_by(temp_sites, date) %>%
  summarise(mean_dir = mean(as.numeric(dir),
            mean_speed = mean(as.numeric(speed))))

save(wind_data, file = "Data/wind_daily.RData")

# load("Data/wind_daily.RData") # Loading the daily wind data for each of the sites
```

@@

# Select only the years 2014 and 2015
filtered_years <- function(df){
  upwelling<- df %>% 
  filter(year(date) %in% seq(2012, 2015)) %>% 
  drop_na()
}

@@

temp_wind <- function(df){
  combined <- df %>% 
  left_join(wind_daily, by = c("site", "date")) %>% 
  #select(-combi) %>% 
  na.trim() %>% 
  group_by(site)
  return(combined)
}

temp_wind_MUR <- temp_wind(df = MUR_fyears) %>% 
  drop_na()
temp_wind_SACTN <- temp_wind(df = SACTN_fyears)
temp_wind_OISST <- temp_wind(df = OISST_fyears)
temp_wind_G1SST <- temp_wind(df = G1SST_fyears)
temp_wind_K10 <- temp_wind(df = K10_fyears)
```

```{r}
histogram_1 <- ggplot(data = temp_wind_MUR, aes(x = dir_circ)) +
geom_histogram() +
facet_wrap(~site, scales = "free_x", ncol = 2)
histogram_1
```

wind_daily <- wind_daily %>% 
  drop_na()
wind_daily_renamed <- wind_daily %>% 
  dplyr::rename(spd = mean_speed) %>%
  dplyr::rename(dir = dir_circ)

p.wr2 <- plot.windrose(data = wind_daily_renamed,
              spd = "spd",
              dir = "dir")
```
